% fodina Humanities LaTeX-/JuraBib-Reference-Learn-Document
%
% (c) Karsten Reincke, Frankfurt a.M. 2010, 2011, ff.
%
% This file is licensed under the Creative Commons Attribution 3.0 Germany
% License (http://creativecommons.org/licenses/by/3.0/de/): 
% For details see teh file LICENSE in the top directory
%
\documentclass[
  DIV=calc,
  BCOR=5mm,
  11pt,
  headings=small,
  oneside,
  abstract=true,
  toc=bib,
  ngerman,english]{scrartcl}

%%% (1) general configurations %%%
\usepackage[utf8]{inputenc}

%%% (2) language specific configurations %%%
\usepackage[]{a4,babel}
\selectlanguage{english}

% package for improving the grey value and the line feed handling
\usepackage{microtype}

%language specific quoting signs
%default for language english is american style of quotes
%\usepackage[english=british]{csquotes}
\usepackage[english=american]{csquotes}

% jurabib configuration
\usepackage[see]{jurabib}
\bibliographystyle{jurabib}
\input{cfg/inc.jbib-cfg.tex}

% language specific hyphenation
\input{cfg/inc.hyphenations.tex}

%%% (3) layout page configuration %%%

% select the visible parts of a page
% S.31: { plain|empty|headings|myheadings }
%\pagestyle{myheadings}
\pagestyle{headings}

% select the wished style of page-numbering
% S.32: { arabic,roman,Roman,alph,Alph }
\pagenumbering{arabic}
\setcounter{page}{1}

% no indent for paragraphs
\setlength{\parindent}{0pt}
\setlength{\parskip}{1.2ex plus 0.2ex minus 0.2ex}


% some additional symbols
\usepackage{amssymb}
\usepackage{stmaryrd}

%- start(footnote-configuration)

% formatting the footnote with koma script tools

\deffootnote[1.5em]{1.5em}{1.5em}{\textsuperscript{\thefootnotemark)\ }}

%integrate nomenclature
\input{cfg/inc.ncl-meta.tex}

% depth of contents
\setcounter{secnumdepth}{5}
\setcounter{tocdepth}{5}

% Hyperlinks
\usepackage{hyperref}
\hypersetup{bookmarks=true,breaklinks=true,colorlinks=true,citecolor=blue,draft=false}

\begin{document}

%% use all entries of the bliography
\nocite{*}

%%-- start(titlepage)
\titlehead{mycsrf.verify-\input{inc.rel.tex}: English}
\subject{(scholar-) Scientific Texts Based on a Modified \textit{jurabib}}
\title{List of defined Usecases}
\subtitle{Comments in Footnotes}
\author{Author\input{cfg/inc.license-fn.tex}}

%thanks entry cannot be combined with license footnote
%\thanks{den Autoren von KOMA-Script und denen von Jurabib}

\maketitle
%%-- end(titlepage)


\begin{description}

  \item[01 \checkmark] book 
    (firstly  mentioned)\footcite[cf.][12]{KantKdU1974} (complete) 
  \item[02 \checkmark] book (directly repeated,
      same page)\footcite[cf.][12]{KantKdU1974} (id., ibid.)
  \item[03 \checkmark] book (directly repeated, 
      other page)\footcite[cf.][13]{KantKdU1974} (id., l.c., p.)
  \item[04 \checkmark] journ. artl.
    (firstly  mentioned)\footcite[cf.][12]{McCarthy1980a} (complete)
  \item[05 \checkmark] journ. artl., (directly repeated,
       same page)\footcite[cf.][12]{McCarthy1980a} (id., ibid.)
  \item[06 \checkmark] journ. artl., (directly repeated,
       other page)\footcite[cf.][13]{McCarthy1980a} (id., l.c., p.)
  
  \item[07 $\lightning$] coll. artl., (firstly  mentioned , 
      new collection)\footcite[cf.][12]{Hays1985a} (both complete)
  \item[08 \checkmark] coll. artl., (directly repeated,
      same page)\footcite[cf.][12]{Hays1985a} (id., ibid.)
      
 \item[09 \checkmark] coll. artl. (directly repeated,
      same page, on the next page)\footcite[cf.][12]{Hays1985a} (short link)
  \item[10 \checkmark]  coll. artl. (directly repeated,
      other page)\footcite[cf.][13]{Hays1985a} (id., l.c., p.)
       
  \item[11 \checkmark] coll. artl. (firstly  mentioned,
      known collection)\footcite[cf.][12]{DaBu1985a} (complete + short)
  \item[12 \checkmark] coll. artl. (directly repeated,
      same page)\footcite[cf.][12]{DaBu1985a} (id., ibid.)

  \item[13 \checkmark] coll. artl. (directly repeated,
      other page)\footcite[cf.][13]{DaBu1985a} (id., l.c., p.)

  \item[14 \checkmark] book with 3-x authors
     (firstly  mentioned)\footcite[cf.][12]{SegEvaTay2009a} (all)
  \item[15 \checkmark] book with 4+x authors
     (firstly  mentioned)\footcite[cf.][12]{HitKroRudSur2008a} (1 + et.al.)

  \item[16 \checkmark]  Coll. with 3-x editors
    (firstly  mentioned)\footcite[cf.][12]{ProcKR2012a} (all)
  \item[17 \checkmark] Coll. with 4+x editors
    (firstly  mentioned)\footcite[cf.][12]{MehDreDesMan2011a} (1 + et.al.)

  
  \item[18 \checkmark] book
    (indirectly repeated)\footcite[cf.][12]{KantKdU1974}  (short link)
  \item[19 \checkmark] journ. artl.
    (indirectly repeated)\footcite[cf.][12]{McCarthy1980a} (short link)
  \item[20 \checkmark] coll. artl.
    (indirectly repeated)\footcite[cf.][12]{Hays1985a} (short link)
  \item[21 \checkmark] man book
    (firstly  mentioned)\footcite[cf.][12]{Kopka2000a} (complete)
  \item[22 \checkmark] man book
    (directly repeated)\footcite[cf.][13]{Kopka2000a} (id., l.c., p.)
   \newpage
  \item[23 \checkmark] woman book
     (firstly  mentioned)\footcite[cf.][12]{Kraemer1988a} (complete)
  \item[24 \checkmark] woman book
    (directly repeated)\footcite[cf.][13]{Kraemer1988a} (\textbf{id.}, l.c., p.)
  \item[25 \checkmark] men book
    (firstly  mentioned )\footcite[cf.][12]{MitGoo2005a} (complete)
  \item[26 \checkmark] men book
    (directly repeated)\footcite[cf.][13]{MitGoo2005a} (\textbf{id.}, l.c., p.)
  \item[27 \checkmark] women book
    (firstly  mentioned)\footcite[cf.][12]{CapMoo2016a} (complete)
  \item[28 \checkmark] women book
    (directly repeated)\footcite[cf.][13]{CapMoo2016a}  (\textbf{id.}, l.c., p.)

  \item[29 \checkmark] MISC
    (firstly  mentioned)\footcite[cf.][12]{Daly2007a} (complete)
  \item[30 \checkmark] MISC
    (directly repeated, same page)\footcite[cf.][12]{Daly2007a} (id., ibid.)
  \item[31 \checkmark]  MISC
    (directly repeated, other page)\footcite[cf.][13]{Daly2007a} (id., l.c.,
    p.)
  \item[32 \checkmark] Electronic
    (firstly  mentioned)\footcite[cf.][12]{Wolter2010a} (complete)
  \item[33 \checkmark]  Electronic
    (directly repeated, same page)\footcite[cf.][12]{Wolter2010a} (id., ibid..)
  \item[34 \checkmark] Electronic
    (directly repeated, other page)\footcite[cf.][13]{Wolter2010a} (id., l.c.,
    p.)
  
  \item[35 \checkmark] MISC
    (indirectly repeated)\footcite[cf.][12]{Daly2007a} (short link)
  \item[36 \checkmark] Electronic,
    (indirectly repeated)\footcite[cf.][12]{Wolter2010a} (short link)
    
  
\end{description}

% insert the nomenclature here

\input{bib/ncl.abbreviations.tex}
\input{bib/ncl.journals.tex}
\printnomenclature

% insert the bibliographical data here
\bibliography{bib/literature}

\end{document}
